---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wodds

<!-- badges: start -->
<!-- badges: end -->

The goal of `wodds` is to make the calculations of whisker odds (wodds) easy.
Whisker odds follow the same rules as letter-values, but with a different naming 
system.

## Installation

You can install the development version of `wodds` from [GitHub](https://github.com) with:

``` r
# install.packages("devtools")
devtools::install_github("alexhallam/wodds")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example 1}
options(digits=1)
library(wodds)
library(knitr)
a <- rnorm(n = 1e4, 0, 1)
df_wodds <- wodds::wodds(a)
df_wodds
```

Works with `knitr::kable` for publications.

```{r example 2}
knitr::kable(df_wodds, align = 'c',digits = 3)
```
